\documentclass[12pt,letterpaper]{article}

% just for the example
\usepackage{lipsum}
% Set margins to 1.5in
\usepackage[margin=1.5in]{geometry}

\usepackage{enumitem}

% for graphics
\usepackage{graphicx}
\graphicspath{{./figures/p3/}}

% for crimson text
\usepackage{crimson}
\usepackage[T1]{fontenc}

% setup parameter indentation
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt}

% for 1.15 spacing between text
\renewcommand{\baselinestretch}{1.15}

% For defining spacing between headers
\usepackage{titlesec}
% Level 1
\titleformat{\section}
  {\normalfont\fontsize{18}{0}\bfseries}{\thesection}{1em}{}
% Level 2
\titleformat{\subsection}
  {\normalfont\fontsize{14}{0}\bfseries}{\thesection}{1em}{}
% Level 3
\titleformat{\subsubsection}
  {\normalfont\fontsize{12}{0}\bfseries}{\thesection}{1em}{}
% Level 4
\titleformat{\paragraph}
  {\normalfont\fontsize{12}{0}\bfseries\itshape}{\theparagraph}{1em}{}
% Level 5
\titleformat{\subparagraph}
  {\normalfont\fontsize{12}{0}\itshape}{\theparagraph}{1em}{}
% Level 6
\makeatletter
\newcounter{subsubparagraph}[subparagraph]
\renewcommand\thesubsubparagraph{%
  \thesubparagraph.\@arabic\c@subsubparagraph}
\newcommand\subsubparagraph{%
  \@startsection{subsubparagraph}    % counter
    {6}                              % level
    {\parindent}                     % indent
    {12pt} % beforeskip
    {6pt}                           % afterskip
    {\normalfont\fontsize{12}{0}}}
\newcommand\l@subsubparagraph{\@dottedtocline{6}{10em}{5em}}
\newcommand{\subsubparagraphmark}[1]{}
\makeatother
\titlespacing*{\section}{0pt}{12pt}{6pt}
\titlespacing*{\subsection}{0pt}{12pt}{6pt}
\titlespacing*{\subsubsection}{0pt}{12pt}{6pt}
\titlespacing*{\paragraph}{0pt}{12pt}{6pt}
\titlespacing*{\subparagraph}{0pt}{12pt}{6pt}
\titlespacing*{\subsubparagraph}{0pt}{12pt}{6pt}

% Set caption to correct size and location
\usepackage[tableposition=top, figureposition=bottom, font=footnotesize, labelfont=bf]{caption}

% set page number location
\usepackage{fancyhdr}
\fancyhf{} % clear all header and footers
\renewcommand{\headrulewidth}{0pt} % remove the header rule
\rhead{\thepage}
\pagestyle{fancy}

% Overwrite Title
\makeatletter
\renewcommand{\maketitle}{\bgroup
   \begin{center}
   \textbf{{\fontsize{18pt}{20}\selectfont \@title}}\\
   \vspace{10pt}
   {\fontsize{12pt}{0}\selectfont \@author} 
   \end{center}
}
\makeatother

% Used for Tables and Figures
\usepackage{float}

% For using lists
\usepackage{enumitem}

% For using APA Citation format
\usepackage{apacite}

% Custom Quote
\newenvironment{myquote}[1]%
  {\list{}{\leftmargin=#1\rightmargin=#1}\item[]}%
  {\endlist}
  
% Create Abstract 
\renewenvironment{abstract}
{\vspace*{-.5in}\fontsize{12pt}{12}\begin{myquote}{.5in}
\noindent \par{\bfseries \abstractname.}}
{\medskip\noindent
\end{myquote}
}

\begin{document}

% Set Title, Author, and email
\title{Assignment P5}
\author{Snejana Shegheva \\ sshegheva3@gatech.edu}

\maketitle
\thispagestyle{fancy}

\section*{Question 1 - Intersection of Technology and Society}

\textit{Our teaching assistants are the lifeblood of this program} - writes David Joyner on one of his emails inviting applications for TA in the OMSCS program. 

Teaching Assistants play an important role in education across all universities, especially the large ones. For a program like OMSCS, that is 100\% remote, the availability of qualified and motivated TAs is even more paramount. Who could have predicted that not only would there be enough applicants willing to contribute, but their applications would be turned away due to overabundance?

The sheer number of TAs with vast experience across many backgrounds who are eager to contribute to a greater education appeared as an \textbf{unexpected positive effect}. My personal skepticism about the success of the program due to its scale and remoteness dissolved largely as a result of my interactions with the TAs from the very beginning of the program. 

Due it its low cost, the OMSCS program attracted a tremendous number of students to the Computer Science field. The sudden accessibility of classes from Computer Science department, might be potentially having a \textbf{negative repercussion} for other departments. I do not have data to substantiate my conclusions, but drawing from my personal experience, I could say that \textit{CS availability} factor played a significant role in my decision making when applying to a Master's Program. If all programs at GaTech would have been equally available, the school of Mathematics would have been my first choice. It would be interesting to forecast number of students in other departments if they would have a similar program and compare it with OMSCS.  

It is understandable that OMSCS was a pilot program, and more are expected to be added in the near future (Online Masters in Analytics has already followed). A great way to \textbf{reduce} the described drawback (before the university can launch more similar programs), is to include more \textbf{electives} in the program from \textbf{different departments}, such as Mathematics, Music, Philosophy, etc. This addition would serve as a bridge to other fields in the university that do not yet offer a similar program. 



\section*{Question 4 - Paper Distillation}

\textbf{Title}: Increasing User's Confidence in Uncertain Data by Aggregating Data from Multiple Sources \cite{greis2017increasing}

The authors take an interesting approach for helping users make more informed decisions in the context there is no sufficient trust in a single source of data. With a goal to reduce the cognitive load for having to compare multiple sources manually, they identify and evaluate a few different \textbf{aggregation mechanisms}. They seek to understand what information can be useful for \textbf{the user} to increase their confidence in decision making. 

What does it mean when the data is \textit{uncertain}? 

When interpreting the data from a \textbf{single} source, the concept of uncertainty is typically related to a statistical uncertainty, such as noisy or anomalous measurements. In this paper, however, the data uncertainty implies the presence of inconsistencies and even conflicts between \textbf{multiple} sources. For example, one weather app may show that it will rain tomorrow, while another app promises a sunny day. If you are planning a hiking trip, the confidence in the forecast is important in making a decision on what gear to take, or whether or not to cancel the trip.  

Is there a gap between service providers and user in terms of trust? Yes. The research shows that general public does not have an intuitive understanding of probabilities, so the service providers who attempt to quantify the uncertainty frequently fail in increasing the user's trust in data.

So, what do the users want? 

According to the two experiments performed by the authors - online survey and an alternative interface designed for comparison - users prefer 1) \textbf{Transparency} that can inform their decisions 2) \textbf{Control} (or a feeling of control) over decisions. The experiments were designed to estimate user's trust in data in tree different setups of data aggregation - direct comparison, aggregating with ranges, aggregating by averaging. 

What are the implications to the interface designers (in applications with uncertain data)?

\hspace{10mm} - Give users control by \textbf{supporting contexts} with different importance. The survey results showed that users prefer more manual/direct comparison in the high-stake situations, such as financial decisions. Giving users the ability to choose different context allows them to make a judgment on how to view and compare data from multiple sources.  

\hspace{10mm} - Anticipate \textbf{different types of users}. The applications should allow users to choose a method of interaction that is suitable to their individual preferences. Some users may choose to tolerate certain levels of uncertainty and use methods that require less mental efforts for interpretation. Other users may prefer an advanced view with options to customize the aspects of their interactions. 

\hspace{10mm} - Establish \textbf{transparency}. Help the user understand the reasoning given by the interface. For example, a service for aggregating news feeds may include the details on the original sources and explanation on how the data has been aggregated. 

The authors of the paper conclude that user's confidence in data increases with additional sources independently of its representation - pictograms, graphs, or text. The comprehension of data changes with the level of aggregation, therefore transparency and flexibility are paramount for gaining user's trust in the scenarios with uncertain data. 

\bibliographystyle{apacite} 
\bibliography{bibtemp}

\end{document}
